|

### 2019-08-07 article/article.Rmd
add text

We use the TDP app to conduct two experimental interventions. We test whether the app has a positive impact on three outcomes of interest: school completion rates, school construction status and complaints to competent authorities. We find that our experiments have delivered mixed results. Two of the findings are positive and in line with our theoretical predictions. From August 2017 to February 2019, TDP increased the likelihood of school completion by 6.8 percent (SE = X.X, t-test = XXX). Additionally, we find that pressure over the bureaucracy increased the investments in the schools by 157.5 percent (SE = X.XX, t-test = XXX). In contrast, our results show the app has a null impact on school constructions statistics. Brazilian politicians did not respond to the citizen's requests placed via the application.

>>>>

We use the TDP app to conduct two experimental interventions and test whether it has an impact on six outcomes related to school completion rates and complains to public authorities. We find that the TDP app increased the likelihood of school completion by 6.8 percent (SE = X.XX, t-test = X.XX) in the first experiment, although the effect is null in the second intervention. Additionally, we find that pressure over the bureaucracy increased the investments in the schools by 157.5 percent (SE = X.XX, t-test = X.XX) in the second experiment. However, our results show that providing information to citizens does not change the percentage invested in all other outcomes.

In contrast, our results show the app has a null impact on school constructions statistics. Brazilian politicians did not respond to the citizen's requests placed via the application.
